Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-09 WRITEUP/ms.tex
type-setting author affiliation stuff

% --------------------------------------------
% \documentclass[twocolumn]{aastex6}
% \documentclass[apj]{emulateapj}
\documentclass[iop]{emulateapj} %iop
\usepackage{amsmath}

@@

\altaffiltext{1}{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, Simons Foundation, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
\altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}
\email{tleung@astro.cornell.edu}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accreting phase (top) and
starburst phase (bottom) compared to
those observed in nearby and the \z$\sim$2 star-forming galaxy.
\label{fig:larsons_single}}
\end{figure*}

@@

% a bit on caveat
While our result, of particular relevance here is the slope of the CMF, is subject
to the uncertainties in the analysis method and the resolution of our simulation --- i.e., that is
we are likely biased to finding more massive clouds.
High resolution simulations will be useful to shed light on
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR; however, they are more expensive to run.
On the contrary, an advantage of using cosmological zoom-in simulations for this study
is that our computational boxes are not closed, allowing us to examine how
the molecular complexes' properties vary under the influence of gas inflow/outflow.

@@

We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
This is consistent with what has been found previously in higher resolution simulation of isolated galaxies \citep{}.
That said, our cosmological zoom-in simulation here allows us to examine 
the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM.

>>>>

% --------------------------------------------
% \documentclass[twocolumn]{aastex6}
% \documentclass[apj]{emulateapj}
\documentclass[iop]{emulateapj} 
\usepackage{amsmath}

@@

\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
\email{tleung@astro.cornell.edu}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
\altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accreting phase (top) and
starburst phase (bottom) compared to
those observed in nearby and the \z$\sim$2 star-forming galaxy.
Red lines show the relation obtained from 
Literature data are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
\label{fig:larsons_single}}
\end{figure*}

@@

% a bit on caveat
While our result, of particular relevance here is the slope of the CMF, is subject
to the uncertainties in the analysis method and the resolution of our simulation --- i.e., that is
we are likely biased to finding more massive clouds.
High resolution simulations will be useful to shed light on
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR; however, they are more expensive to run.
On the contrary, an advantage of using cosmological zoom-in simulations for this study
is that our computational boxes are not closed, allowing us to examine how
the molecular complexes' properties vary under the influence of gas inflow/outflow 
(see e.g., \citealt{Klessen10a, Goldaum11a}). % turbulence when disk still accreting gas

@@

We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
This is consistent with what has been found previously in higher resolution simulation of isolated galaxies \citep{}.
That said, our cosmological zoom-in simulation here allows us to examine 
the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldaum11a}).
